---
title: "AutoSolver"
output: 
  html_notebook:
    toc: TRUE
---

# Introduction
This is a test based on [this post](https://blog.computationalcomplexity.org/2018/04/find-8-digits-number-such-that.html).

The point lies in forming such 8-digit number that acts as the following, from left to right:

* first digit contains the number of unique digits among the seven others;
* second digit figures the number of _6_;
* third digit figures the number of _5_;
* fourth digit figures the number of _4_;
* fifth digit figures the number of _3_;
* seventh digit figures the number of _1_;
* eighth digit figures the number of _0_.

This type of problem can be solved with brute force, trying every kind of combination to meet the conditions.

> Basically 10^8 digits to test. It could be interesting, although my computing power is definietly not enough.

# Finding ways

The trick would consist to apply those rules to a given random number, and then to see if this converges to a specific number.

If such number exist, one would also want to find if more exist, and to count the number of hops/iterations to get there.


## Imports

I somehow got used to data.table and ggplot2 packages, so let us deal with it.

```{r message=FALSE, warning=FALSE}
# Import
library(data.table)
library(ggplot2)
```

## Proof of concept

Remember applying the test to a random eight-number digit?

```{r}
# Starting number
nb <- as.list(sample(0:9,8,replace=TRUE))
# Fist loop
fn <- list(0,
           sum(nb==6),
           sum(nb==5),
           sum(nb==4),
           sum(nb==3),
           sum(nb==2),
           sum(nb==1),
           sum(nb==0))

fn[1]<- length(unique(fn[-1])) # Counting different unique digits

print(paste(nb,collapse=""))
print(paste(fn,collapse=""))
```

It does produce something. Although, will this converge? Loop is the key.

```{r}
i<-0 # Hops   
while (sum(abs(mapply(FUN = function(nb,fn) {sum(as.numeric(nb -fn))},nb=nb,fn=fn)))!=0) {
    nb <- fn
    fn <- list(0,
               sum(nb==6),
               sum(nb==5),
               sum(nb==3),
               sum(nb==1),
               sum(nb==2),
               sum(nb==4),
               sum(nb==0))
    
    fn[1]<- length(unique(fn[-1]))
    
    i<-i+1
}

print(i)
print(paste(fn,collapse=""))

```

A reasonnable number of hops, smaller than _20_, that lead to _40013112_. Feel free to check. 

Questions are: would there be other numbers? How many hops are required to converge? Is convergence always possible?

## The high road

```{r}
# To keep result
res <- setNames(data.table(matrix(ncol=3,nrow=0)),c("Ini","Fin","Hop"))

# Init
st <- Sys.time()
for (j in 1:10000) {
  
  de <- as.list(sample(0:9,8,replace=TRUE))
  nb <- as.list(de)
  fn <- list(length(unique(nb)),
             sum(nb==6),
             sum(nb==5),
             sum(nb==4),
             sum(nb==3),
             sum(nb==2),
             sum(nb==1),
             sum(nb==0))
  
  i <-0
  
  while (sum(abs(mapply(FUN = function(nb,fn) {sum(as.numeric(nb -fn))},nb=nb,fn=fn)))!=0) {
    nb <- fn
    fn <- list(0,
               sum(nb==6),
               sum(nb==5),
               sum(nb==3),
               sum(nb==1),
               sum(nb==2),
               sum(nb==4),
               sum(nb==0))
    
    fn[1]<- length(unique(fn[-1]))
    
    i<-i+1
  }
  
  # Adding to res
  te <- setNames(data.table(paste(de,collapse=""),paste(fn,collapse =""),i),c("Ini","Fin","Hop"))
  res <- rbind.data.frame(res,te,make.row.names = FALSE)
  
}
print(Sys.time()-st)
```

# And so?

_res_ contains _10^5 observations_. That's great. Apparently, everything did converge.

```{r}
summary(res$Hop)
```
Everything converged rather quickly... What values?


```{r}
summary(factor(res$Fin))
```

So basically every attempt converged to the same value? Was the random generator broken?
